\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-01 paper/paper.Rnw
Citations

>>>>

The models used for this paper were generated using SAS software, Version 9 of the SAS System for Unix with the MIXED and GLIMMIX procedures. Copyright \©2015 SAS Institute Inc. SAS and all other SAS Institute Inc. product or service names are registered trademarks or trademarks of SAS Institute Inc., Cary, NC, USA.

Further analysis was carried out using \citet{R} version 3.1.2 and \cited{RStudio} version 0.99.484 using the packages: \citet{dplyr}, \citet{ggplot2}, \citet{grid}, \citet{gridExtra}, \citet{gridSVG}, \citet{knitr}, \citet{maps}, \citet{mFilter}, \citet{mnormt}, \citet{nullabor}, \citet{stringr} and \citet{tidyr}.
